Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-10 paper.tex
First version of story model fragment.  Blows our page budget! (sigh)

\section{A Lesson from Nell}
\begin{figure}
\centering
\epsfig{file=roger1.eps, height=1.5in} % width=3.2in
\caption{Illustration of Nell's primary interface.}\label{fig:nell}
\end{figure}

% tell a nell story up front
Miles from the nearest school, a young Ethiopian girl turns on a
tablet computer for the first time.  The solar-powered machine begins
talking to her immediately: \textit{``Hello!  Would you like to hear a story?''}

@@

@@

\begin{figure}
\centering
\epsfig{file=xo3-3.eps, width=3.2in}
\caption{Nell's solar-powered hardware platform.  The tablet design
  allows for direct interaction.}\label{fig:xo3}
\end{figure}

@@

\subsection{Rule-based story modules}
Narrative is the core of the Nell interface.  It is important that
Nell's story be modular and extensible.  We use a rule-based story
model with programmable conflict resolution to provide this ability.
Figure~\ref{fig:rules} shows an excerpt of the story module driving
the interaction described in the introduction to this paper.

@@

\section{Acknowledgments}
Nell's design evolved from experience with the Sugar system,
architected by Walter Bender, and through stimulating discussions with
Chris Ball and Angela Chang.  Michael Stone also contributed to an
early implementation.

>>>>

\section{A Lesson from Nell}
\begin{figure}
\centering
\epsfig{file=xo3-3.eps, width=3.2in}
\caption{Nell's solar-powered hardware platform.  The tablet design
  allows for direct interaction.}\label{fig:xo3}
\end{figure}
% tell a nell story up front
Miles from the nearest school, a young Ethiopian girl turns on a
tablet computer for the first time.  The solar-powered machine begins
talking to her immediately: \textit{``Hello!  Would you like to hear a story?''}

@@

\begin{figure}
\centering
\epsfig{file=roger1.eps, height=1.5in} % width=3.2in
\caption{Illustration of Nell's primary interface.}\label{fig:nell}
\end{figure}

@@

@@

\subsection{Rule-based story modules}
\begin{figure*}
\begin{verbatim}
{ world: {
    id: "/nell.laptop.org/chapters/alphabet-book" // canonical URL for this module
    scene: "opening", // initial scene
  }, actors: [
    // these characters are common to different modules
    { id: "user", type: "/nell.laptop.org/characters/user" },
    { id: "princess", type: "/nell.laptop.org/characters/nell" }
  ], scenes: [
    { id: "opening", // http://nell.laptop.org/chapters/alphabet-book/scenes/opening
      subject: "actors/princess", verb: "speak", object: "actors/user",
      text: "Hello!  Would (o/2) like to hear a story?" },
    { id: "story-1",
      cond: rule`At(opening) && Event(Chat, Yes)`,
      subject: "actors/princess", verb: "speak", object: "actors/user",
      text: "Once upon a time..." },
    ...
    { id: "r-drawn",
      cond: rule`Event(Activity, DrawR)`,
      subject: "actors/princess", verb: "speak", object: "actors/user",
      text: "Very good, (o/3)!",
      action: js`startAnimation("r-runs")` },
    ...
  ]
}
\end{verbatim}
\caption{Excerpt of JSON-formatted story module.  Some details (format
  versioning, etc) have been elided).}\label{fig:rules}
\end{figure*}
Narrative is the core of the Nell interface.  It is important that
Nell's story be modular and extensible.  We use a rule-based story
model with programmable conflict resolution to provide this ability.
Figure~\ref{fig:rules} shows an excerpt of the story module driving
the interaction described in the introduction to this paper.

@@

\section{Acknowledgments}
Nell's design evolved from experience with the Sugar system,
architected by Walter Bender, and through stimulating discussions with
Chris Ball and Angela Chang.  Chris Ball and Michael Stone contributed
to an implementation of the rule-based story model.
